Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-15 csf-2017/paper.tex
A (final?) missing piece of the RW.

@@

Other papers that enforce well-bracketed control flow at low level (using a
trusted stack manager)
\begin{itemize}
\item \cite{patrignani_modular_2016-1}
\item \cite{juglaret_beyond_2016-1}
\item other stuff?
\end{itemize}
CFI: 
\begin{itemize}
\item \cite{budiu_architectural_2006,abadi_control-flow_2005}
\end{itemize}

>>>>

In this section, we summarise how our work relates to previous work. We do not
repeat the work already discussed in Section~\ref{sec:discussion}.

@@

There are plenty of other papers that enforce well-bracketed control flow at a
low level, but most are restricted to preventing particular types of attacks and
enforce only partial correctness of control flow. This includes particularly the
line of work on \emph{control flow integrity}~\citep{abadi_control-flow_2005}.
This work uses a quite different attacker model than us: they assume an attacker
that is not able to execute code, but can overwrite arbitrary data at any time
during execution (as a model for buffer overflows). By checking the address of
every indirect jump and using memory access control to prevent overwriting code,
this work enforces what they call control flow integrity, formalised as the
property that every jump will follow a legal path in the control flow graph.
As discussed in Section~\ref{sec:discussion}, this correctness property does not
take into account temporal properties and seems hard to use for reasoning.

More closely related to our work are papers that use a trusted stack manager and
some form of memory isolation to enforce control flow correctness as part of a
secure compilation
result~\citep{patrignani_modular_2016-1,juglaret_beyond_2016-1}. Our work
differs from theirs in that we use a different form of low-level security
primitive (a capability machine with local capabilities rather than a machine
with a primitive notion of compartments) and we do not use a trusted stack
manager component, but a decentralised calling convention based on local
capabilities. Also, they both prove a secure compilation result from a
high-level language, which clearly implies a general form of control flow
correctness, while we define a sound logical relation that can be used to reason
about specific programs that rely on well-bracketed control flow.
